\chapter{Requirements Traceability}

This chapter outlines the traceability framework implemented to maintain alignment between the project objectives, stakeholder needs, and the final deliverables. Establishing clear links between requirements, design, implementation, and testing minimizes the risk of unfulfilled specifications and promotes a transparent development process.

\textbf{[R1]} The system allows unregistered users to create an account.  
\begin{itemize}
    \item \textbf{WebApp:} Provides the user interface for new users to enter their registration details.
    \item \textbf{AccountManager:} Manages the account creation process, validates user details and ensures proper storage of data.
    \item \textbf{AuthenticationManager:} Verifies that the registration process complies with security protocols.
    \item \textbf{DataManager:} Handles the storage of new user data in the database.
    \item \textbf{NotificationManager:} Sends notifications to users about the successful creation of their accounts.
    \item \textbf{EmailServiceProvider:} Sends email confirmation or verification messages to new users.
    \item \textbf{DBMS:} Stores all account information securely in the database.
\end{itemize}

\textbf{[R2]} The system allows students to upload their CV.  
\begin{itemize}
    \item \textbf{WebApp:} Provides the interface for students to upload their CVs.
    \item \textbf{AccountManager:} Ensures that only authenticated students can upload their CVs.
    \item \textbf{AuthenticationManager:} Validates the session and permissions of the student uploading the CV.
    \item \textbf{DataManager:} Stores the uploaded CV securely in the database.
    \item \textbf{StatisticalAnalysisToolManager:} Analyzes the CV to improve recommendations and provide insights for better matching.
    \item \textbf{DBMS:} Stores CV data for future reference and analysis.
\end{itemize}

\textbf{[R3]} The system allows companies to publish new internships.  
\begin{itemize}
    \item \textbf{WebApp:} Provides the interface for companies to add new internship postings.
    \item \textbf{AccountManager:} Ensures only authenticated company representatives can post internships.
    \item \textbf{AuthenticationManager:} Verifies that the company representative has the necessary permissions.
    \item \textbf{DataManager:} Stores the internship postings in the database.
    \item \textbf{StatisticalAnalysisToolManager:} Analyzes the internship postings to match them with student profiles.
    \item \textbf{DBMS:} Safely stores internship data for future searches and recommendations.
\end{itemize}

\textbf{[R4]} The system allows companies to add a description to their internships.  
\begin{itemize}
    \item \textbf{WebApp:} Provides the interface for adding detailed descriptions to internships.
    \item \textbf{AccountManager:} Verifies that authenticated companies can update internship details.
    \item \textbf{AuthenticationManager:} Checks permissions for modifying internship descriptions.
    \item \textbf{DataManager:} Updates and stores the descriptions in the database.
    \item \textbf{StatisticalAnalysisToolManager:} Analyzes the internship descriptions to match them with student profiles.
    \item \textbf{DBMS:} Safely records the updated internship details.
\end{itemize}

\textbf{[R5]} The system allows students to browse available internships.  
\begin{itemize}
    \item \textbf{WebApp:} Displays a list of internships for students to browse through.
    \item \textbf{ApplicationManager:} Manages the search and retrieval of available internships.
    \item \textbf{StatisticalAnalysisToolManager:} Analyzes browsing trends and preferences to refine recommendations.
    \item \textbf{DataManager:} Retrieves and organizes internship data for display.
    \item \textbf{DBMS:} Stores internship details to facilitate searches and retrievals.
\end{itemize}

\textbf{[R6]} The system allows users to filter internships when performing a search.  
\begin{itemize}
    \item \textbf{WebApp:} Provides filtering options for criteria such as location, domain, and duration.
    \item \textbf{ApplicationManager:} Processes search queries and applies filters to display relevant results.
    \item \textbf{StatisticalAnalysisToolManager:} Enhances filtering by analyzing patterns in user preferences.
    \item \textbf{DataManager:} Applies filter criteria to the database and retrieves relevant results.
    \item \textbf{DBMS:} Stores filterable data for internships, enabling detailed searches.
\end{itemize}

\textbf{[R7]} When finding an internship that suits their interests, the system allows students to apply for it.  
\begin{itemize}
    \item \textbf{WebApp:} Enables students to submit their applications through the platform.
    \item \textbf{ApplicationManager:} Manages the submission of applications and notifies the relevant company.
    \item \textbf{StatisticalAnalysisToolManager:} Tracks application data to refine matching and recommendations.
    \item \textbf{AuthenticationManager:} Verifies the permissions and authenticity of the student applying.
    \item \textbf{NotificationManager:} Notifies both the student and the company about the application status.
    \item \textbf{EmailServiceProvider:} Sends confirmation emails to both parties regarding the application.
    \item \textbf{DataManager:} Processes and records application data for audit and tracking purposes.
    \item \textbf{DBMS:} Stores applications securely for reference and analysis.
\end{itemize}

\textbf{[R8]} When finding a CV that suits their interests, the system allows companies to request that student's application.  
\begin{itemize}
    \item \textbf{WebApp:} Allows companies to request applications from students through the interface.
    \item \textbf{ApplicationManager:} Processes company requests and sends notifications to the respective students.
    \item \textbf{StatisticalAnalysisToolManager:} Updates its data based on the company’s preferences and feedback.
    \item \textbf{AuthenticationManager:} Verifies the company's permissions before granting access to student data.
    \item \textbf{NotificationManager:} Notifies students about application requests from companies.
    \item \textbf{EmailServiceProvider:} Sends email notifications to students regarding company interest.
    \item \textbf{DataManager:} Tracks requests for applications and ensures data integrity.
    \item \textbf{DBMS:} Stores records of application requests and student profiles for future reference.
\end{itemize}

\textbf{[R9]} When a new internship that might interest some students becomes available, the system notifies them.  
\begin{itemize}
    \item \textbf{WebApp:} Displays notification messages to students about new internships.
    \item \textbf{RecommendationManager:} Handles the new match found.
    \item \textbf{StatisticalAnalysisToolManager:} Analyzes new internships and matches them with student profiles.
    \item \textbf{NotificationManager:} Sends real-time notifications about new opportunities.
    \item \textbf{EmailServiceProvider:} Sends email alerts to students about new internships.
    \item \textbf{DataManager:} Updates the database with new internship information and matches.
    \item \textbf{DBMS:} Stores and indexes notifications and recommendation data.
\end{itemize}

\textbf{[R10]} When a student's CV that corresponds to a company's needs becomes available, the system informs them.  
\begin{itemize}
    \item \textbf{WebApp:} Provides a dashboard where companies can view matched CVs.
    \item \textbf{EmailServiceProvider:} Sends notifications to companies regarding matching CVs.
    \item \textbf{StatisticalAnalysisToolManager:} Finds matches between a student’s CV and internships descriptions posted by the company.
    \item \textbf{DataManager:} Accesses both the student's CV and the company's internship descriptions.
    \item \textbf{RecommendationManager:} Handles the new match found.
    \item \textbf{NotificationManager:} Sends notifications to the company once a matching CV is found.
    \item \textbf{AuthenticationManager:} Ensures the company has appropriate access permissions.
    \item \textbf{DBMS:} Stores matching data securely and makes it accessible for visualization.
\end{itemize}

\textbf{[R11]} The system allows students to accept a recommendation, applying for that particular internship. 
\begin{itemize}
    \item \textbf{WebApp:} Provides an interface for students to view and accept recommendations.
    \item \textbf{EmailServiceProvider:} Sends confirmation emails upon recommendation acceptance.
    \item \textbf{Recommendation Manager:} Handles the new match found.
    \item \textbf{Data Manager:} Retrieves recommendations linked to the student's profile.
    \item \textbf{Application Manager:} Sends and manages the student's application after accepting the recommendation.
    \item \textbf{Authentication Manager:} Ensures the user is logged in with a student account and has privileges to perform this action.
    \item \textbf{Statistical Analysis Tool Manager:} Records acceptance feedback to improve the matching algorithm.
    \item \textbf{DBMS:} Stores all associated recommendation and application data securely.
\end{itemize}

\textbf{[R12]} The system allows companies to accept a recommendation, inviting the candidate that was proposed.
\begin{itemize}
    \item \textbf{WebApp:} Provides an interface for companies to view and accept recommendations.
    \item \textbf{EmailServiceProvider:} Sends invitations to students after company acceptance.
    \item \textbf{Recommendation Manager:} Handles the new match found.
    \item \textbf{Data Manager:} Retrieves recommendations linked to the company profile.
    \item \textbf{Notification Manager:} Notifies the proposed candidate of the company's acceptance.
    \item \textbf{Authentication Manager:} Ensures the company is logged in with the appropriate account and privileges.
    \item \textbf{Statistical Analysis Tool Manager:} Records acceptance feedback to refine recommendations.
    \item \textbf{DBMS:} Stores data related to company recommendations securely.
\end{itemize}

\textbf{[R13]} The system allows students to accept an invitation of a company for a particular internship, applying for it.
\begin{itemize}
    \item \textbf{WebApp:} Provides an interface for students to view and accept invitations.
    \item \textbf{EmailServiceProvider:} Sends confirmation emails upon invitation acceptance.
    \item \textbf{Application Manager:} Manages the submission of the internship application after invitation acceptance.
    \item \textbf{Notification Manager:} Sends notifications confirming the invitation acceptance.
    \item \textbf{Data Manager:} Retrieves invitations linked to the student's profile.
    \item \textbf{Authentication Manager:} Verifies the user's privileges and account type.
    \item \textbf{Statistical Analysis Tool Manager:} Records feedback to enhance the recommendation system.
    \item \textbf{DBMS:} Stores all related invitation and application data securely.
\end{itemize}

\textbf{[R14]} When the two parties have accepted a recommendation, or when an application or invitation is accepted, the system allows them to establish contact.
\begin{itemize}
    \item \textbf{WebApp:} Provides an interface for users to exchange contact details or initiate communication.
    \item \textbf{EmailServiceProvider:} Sends confirmation and contact-sharing emails.
    \item \textbf{Statistical Analysis Tool Manager:} Records interaction data for analytics.
    \item \textbf{Notification Manager:} Notifies users when contact is established.
    \item \textbf{Interview Manager:} Assists in scheduling meetings or interviews as needed.
    \item \textbf{Authentication Manager:} Ensures that users have appropriate privileges.
    \item \textbf{Data Manager:} Retrieves and stores contact interaction data.
    \item \textbf{DBMS:} Maintains records of all communication actions securely.
\end{itemize}

\textbf{[R15]} When conducting an interview, the system supports the companies with the interview process.  
\begin{itemize}
    \item \textbf{WebApp:} Provides an interface for companies to schedule, manage, and track interviews.  
    \item \textbf{EmailServiceProvider:} Sends interview invitations, reminders, and updates to both students and companies.  
    \item \textbf{Interview Manager:} Handles interview scheduling, tracking progress, and managing interview-related interactions.  
    \item \textbf{Notification Manager:} Sends reminders about upcoming interviews and updates on interview outcomes.  
    \item \textbf{Statistical Analysis Tool Manager:} Analyzes feedback and data from the interview process to refine the system.  
    \item \textbf{Authentication Manager:} Ensures only authorized users can schedule and manage interviews.  
    \item \textbf{Data Manager:} Stores and retrieves interview data such as schedules, feedback, and outcomes.  
    \item \textbf{DBMS:} Maintains secure records of all interview-related data.  
\end{itemize}  

\textbf{[R16]} When conducting an interview, the system supports the companies with the finalization of the selection.  
\begin{itemize}
    \item \textbf{WebApp:} Allows companies to update the interview outcomes and finalize selections.  
    \item \textbf{EmailServiceProvider:} Notifies students about their selection status.  
    \item \textbf{Interview Manager:} Tracks interview progress and helps finalize decisions.  
    \item \textbf{Notification Manager:} Informs students of the final decision, whether selected or not.  
    \item \textbf{Data Manager:} Stores final selection details and related data.  
    \item \textbf{DBMS:} Securely manages selection outcomes and records for future reference.  
\end{itemize}  

\textbf{[R17]} The system allows students and companies to provide feedback and suggestions to perform statistical analysis.  
\begin{itemize}
    \item \textbf{WebApp:} Provides a feedback submission form for both students and companies.  
    \item \textbf{EmailServiceProvider:} Sends reminders to submit feedback.  
    \item \textbf{Feedback Manager:} Collects and organizes feedback data for analysis.  
    \item \textbf{Statistical Analysis Tool Manager:} Processes feedback to generate actionable insights.  
    \item \textbf{Notification Manager:} Requests feedback and confirms submission to users. 
    \item \textbf{Authentication Manager:} Ensures only authorized users can provide feedback.  
    \item \textbf{Data Manager:} Stores feedback securely for statistical analysis.  
    \item \textbf{DBMS:} Maintains all feedback records securely.  
\end{itemize}  

\textbf{[R18]} The system provides suggestions to students regarding how to make their CVs more appealing.  
\begin{itemize}
    \item \textbf{WebApp:} Displays personalized CV improvement suggestions.  
    \item \textbf{EmailServiceProvider:} Sends suggestions via email.  
    \item \textbf{Statistical Analysis Tool Manager:} Analyzes CV data and trends to generate suggestions.  
    \item \textbf{Account Manager:} Updates and manages the student’s CV in the system.  
    \item \textbf{Data Manager:} Accesses CV and job requirement data for analysis.  
    \item \textbf{Notification Manager:} Notifies students about CV improvement recommendations.  
    \item \textbf{DBMS:} Stores CV data securely for further analysis.  
\end{itemize}  

\textbf{[R19]} The system provides suggestions to companies regarding how to make their project descriptions more appealing.  
\begin{itemize}
    \item \textbf{WebApp:} Displays personalized project description suggestions.  
    \item \textbf{EmailServiceProvider:} Sends suggestions via email.  
    \item \textbf{Statistical Analysis Tool Manager:} Analyzes project description trends to generate improvement suggestions.  
    \item \textbf{Account Manager:} Updates and manages project descriptions in the system.  
    \item \textbf{Data Manager:} Accesses project and CV data for analysis.  
    \item \textbf{Notification Manager:} Notifies companies about improvement recommendations.  
    \item \textbf{DBMS:} Stores project description data securely for further analysis.  
\end{itemize}  

\textbf{[R20]} During the matchmaking process, the system allows all users to keep track of its execution and outcome.  
\begin{itemize}
    \item \textbf{WebApp:} Provides a dashboard to track matchmaking progress and results.  
    \item \textbf{EmailServiceProvider:} Sends updates on matchmaking status.  
    \item \textbf{Recommendation Manager:} Monitors and displays matchmaking outcomes.  
    \item \textbf{Statistical Analysis Tool Manager:} Offers detailed insights into matchmaking efficiency.  
    \item \textbf{Notification Manager:} Updates users in real-time on matchmaking progress.   
    \item \textbf{Authentication Manager:} Ensures secure access to matchmaking data.  
    \item \textbf{DBMS:} Stores matchmaking data securely.  
\end{itemize}  

\textbf{[R21]} During the internship, the system allows all interested parties to monitor it.  
\begin{itemize}
    \item \textbf{WebApp:} Provides an interface for monitoring internship progress.  
    \item \textbf{EmailServiceProvider:} Sends periodic updates on the internship.  
    \item \textbf{Overview Manager:} Tracks and displays ongoing internship updates.  
    \item \textbf{Notification Manager:} Alerts stakeholders about internship milestones or issues.  
    \item \textbf{Data Manager:} Records and retrieves internship monitoring data.  
    \item \textbf{Authentication Manager:} Ensures secure access to monitoring features.  
    \item \textbf{DBMS:} Maintains records of internship progress securely.  
\end{itemize}  

\textbf{[R22]} During an ongoing internship, the system allows all users to complain.  
\begin{itemize}
    \item \textbf{WebApp:} Provides a complaint submission interface.  
    \item \textbf{EmailServiceProvider:} Sends complaint submission confirmations and updates.  
    \item \textbf{Overview Manager:} Logs and tracks complaints.  
    \item \textbf{Notification Manager:} Notifies relevant parties about complaints.  
    \item \textbf{Authentication Manager:} Validates the identity and permissions of users submitting complaints.  
    \item \textbf{Data Manager:} Stores complaints for resolution.  
    \item \textbf{DBMS:} Maintains a secure record of complaints.  
\end{itemize}  

\textbf{[R23]} During an ongoing internship, the system allows all users to communicate problems.  
\begin{itemize}
    \item \textbf{WebApp:} Enables problem reporting through a dedicated interface.  
    \item \textbf{EmailServiceProvider:} Sends updates on reported problems.  
    \item \textbf{Overview Manager:} Facilitates problem resolution and tracking.  
    \item \textbf{Notification Manager:} Updates stakeholders on problem status and resolution.  
    \item \textbf{Authentication Manager:} Ensures only authorized users can report issues.  
    \item \textbf{Data Manager:} Logs reported problems securely.  
    \item \textbf{DBMS:} Stores problem reports and updates securely.  
\end{itemize}  

\textbf{[R24]} During an ongoing internship, the system allows all users to provide information on its status.  
\begin{itemize}
    \item \textbf{WebApp:} Offers forms for submitting internship status updates.  
    \item \textbf{EmailServiceProvider:} Notifies stakeholders about new updates.  
    \item \textbf{Overview Manager:} Tracks status updates and displays them to relevant parties.  
    \item \textbf{Notification Manager:} Alerts stakeholders about status changes.  
    \item \textbf{Data Manager:} Records and retrieves status updates.  
    \item \textbf{Authentication Manager:} Verifies user permissions for updating internship status.  
    \item \textbf{DBMS:} Secures all status-related records.  
\end{itemize}  

\textbf{[R25]} When reports or complaints about the status of an ongoing internship are made, the system allows Universities to see them.  
\begin{itemize}
    \item \textbf{WebApp:} Provides a dashboard for viewing reports and complaints.  
    \item \textbf{EmailServiceProvider:} Notifies universities about new reports or complaints.  
    \item \textbf{Overview Manager:} Displays reports and complaints for university review.  
    \item \textbf{Notification Manager:} Alerts universities about updates on complaints.  
    \item \textbf{Data Manager:} Retrieves stored complaints for review.  
    \item \textbf{Authentication Manager:} Restricts access to authorized university representatives.  
    \item \textbf{DBMS:} Maintains secure complaint records.  
\end{itemize}  

\textbf{[R26]} When complaints about the status of an ongoing internship are made, the system allows Universities to handle them.  
\begin{itemize}
    \item \textbf{WebApp:} Enables universities to address complaints via a dedicated interface.  
    \item \textbf{EmailServiceProvider:} Notifies users about complaint resolutions.  
    \item \textbf{Overview Manager:} Tracks resolution progress and logs actions.  
    \item \textbf{Notification Manager:} Updates stakeholders on complaint resolution progress.  
    \item \textbf{Data Manager:} Stores resolution details and actions.  
    \item \textbf{Authentication Manager:} Ensures only authorized university staff handle complaints.  
    \item \textbf{DBMS:} Secures records of complaint resolutions.  
\end{itemize}  
